An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-08-03 poly-embed-journal/poly-embed-journal.tex
notes on sec 4

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
\S~\ref{app:calibration} contains the full proof; this section provides a sketch of the main construction and result.

@@

The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
Because $u$ minimizes expected loss for both $p$ and $p'$, this imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
It is not \emph{a priori} clear that these sets even have a nonempty intersection.
We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e. if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.

@@

The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
We do so by ``thickening'' the link by $\epsilon$ as described next.
Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
Then, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty.
%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.

>>>>

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss, which we summarize in the following theorem.
\S~\ref{app:calibration} contains the full proof; this section provides a sketch of the main construction and result.

@@

\raf{I liked the new version in general.  The only thing I was suggest is that for a journal version we could add a bit more detail right here, in the proof sketch.  For example, maybe a high-level overview right at this spot would help, since when you launch into step 1, it's not clear how many steps will follow.  And after step 2, there is a definition, and more discussion after.  All the pieces are great; maybe just a splash of overview and organization can help the reader orient as they go through it.}

The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
It is not \emph{a priori} clear that these sets even have a nonempty intersection.
We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e. if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.

@@

The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
We do so by ``thickening'' the link by $\epsilon$ as described next.
Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
Then, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.
